Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-17 Docs/IJES/journal.tex
minor changes

If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler. \textcolor{blue}{However, ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free. However, it is possible to use free GA and ILP libraries (BSD-Style and MIT licenses) as well.}

>>>>

If considering off-the-shelf tools, as MATLAB to ILP and GA, the coding is simpler. \textcolor{blue}{ESBMC and $\nu$Z have BSD-Style and MIT licenses, respectively and can be downloaded and used for free. Similarly, it is also possible to use free GA and ILP libraries (BSD-Style and MIT licenses) for different programing languages.}
